---
title: "Post #2: Open Sesame"
description: |
  Maneuvering through Oauth2 for API access
author:
  - name: Jacob Corbridge
    url: https://www.linkedin.com/in/jacobcorbridge/
date: 05-12-2021
output:
  distill::distill_article:
    self_contained: false
---

```{r include=FALSE}
library(png)
library(grid)
```

```{r, echo=FALSE}
library(reticulate)
library(ggplot2)

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  out.width = "70%",
  fig.align = 'center',
  fig.width = 6,
  fig.asp = 0.618,  # 1 / phi
  fig.show = "hold",
  cache = FALSE,
  engine.path = 'C:\\Users\\Jacob Corbridge\\AppData\\Local\\Programs\\Python\\Python39',
  python.reticulate = TRUE,
  message = FALSE,
  warning = FALSE
)

requests <- import('requests')
json <- import('json')
numpy <- import('numpy')
urllib3 <- import('urllib3')


```

```{python, echo=FALSE}
import pandas as pd
import requests
import json
import numpy as np
import urllib3
```


Getting Authorized seems to be the most complicated and annoying part of the data access process. Authorization requires seveal codes and ID's, and access only lasts for 12 hours before the process needs to be repeated. If this process is ever to be automated, those issues will certainly need to be addressed. Lucky for us, that is for another time. 

To begin, we need to import libraries and declare client info. 

```python
from requests_oauthlib import OAuth2Sessions
import requests
import pandas as pd
```

```python
CLIENT_ID = 'place_client_id_here'
CLIENT_SECRET = 'place_client_secret_here'
CLIENT_REDIRECT_URI = 'place_client_redirect_uri_here'
```

Once we've done that. we will need to simply run some code provided. We will need the Token Grant URL and the Authorization URL to get and authorization code and access token. This chunk also displays our available scopes, or what level of data access we have. 

```python
WELL_KNOWN_URL = 'https://signin.johndeere.com/oauth2/aus78tnlaysMraFhC1t7/.well-known/oauth-authorization-server'

# Query the ./well-known OAuth URL and parse out the authorization URL, the token grant URL, and the available scopes
well_known_response = requests.get(WELL_KNOWN_URL)
well_known_info = json.loads(well_known_response.text)

AUTHORIZATION_URL = well_known_info['authorization_endpoint']
TOKEN_GRANT_URL = well_known_info['token_endpoint']
AVAILABLE_SCOPES = str(' ').join(well_known_info['scopes_supported'])

print('Well Known Authorization URL - ' + AUTHORIZATION_URL)
print('Well Known Token Grant URL - ' + TOKEN_GRANT_URL)
print('Available Scopes - ' + AVAILABLE_SCOPES)
```

Next we request an Authorization Code, and a link to Develop with Deere is provided.

```python
SCOPES_TO_REQUEST = {'offline_access', 'ag1', 'eq1', 'files', 'ag2', 'org1'}
STATE = "Some Unique Identifier"
oauth2_session = OAuth2Session(CLIENT_ID,  redirect_uri=CLIENT_REDIRECT_URI, scope=SCOPES_TO_REQUEST)

authorization_request, state = oauth2_session.authorization_url(AUTHORIZATION_URL, STATE)
print("Click on the following link to present the user with sign in form where they authenticate and approve access to your application.")
print(authorization_request) 
```

Here we'll copy the code provided within the URL of the website

```{r, echo=FALSE}
img <- readPNG('C:/Users/Jacob Corbridge/Documents/Senior Project/jacobcorbridge97.github.io/Project_Photos/authorization_url.png')
grid.raster(img)
```

And paste it here.

```python
### Update the authorization code here
AUTHORIZATION_CODE = 'place_authorization_code_here'

# Leave the line below as-is. This is to make sure that you have update the AUTHORIZATION_CODE
assert(AUTHORIZATION_CODE != 'place_authorization_code_here'), 'The AUTHORIZATION_CODE in this cell must be replaced by the authorization_code that you recieved'

### Now that we have an authorization code, let's fetch an access and refresh token
token_response = oauth2_session.fetch_token(TOKEN_GRANT_URL, code=AUTHORIZATION_CODE, client_secret=CLIENT_SECRET)
access_token = token_response['access_token']
refresh_token = token_response['refresh_token']

# Also take note that the access token expiration time is returned.  When the access token expires, 
# you will want to use the refresh token to request a new access token (described later in this notebook)
access_token_expiration = token_response['expires_in']

print("Access Token: " + access_token)
print("Refresh Token: " + refresh_token)
print("Hours Token Is Valid: " + str(int(access_token_expiration/60/60)))
```

We now have our access token, we'll need that later when we attempt to make a call.

We are now authenticated and are free to invoke the API however we want. Thank goodness that is over. 
The code below will now connect to the sandbox API.


```python
### Create Connections Link
URL = 'https://connections.deere.com/connections/' + CLIENT_ID + '&redirect_uri=' + CLIENT_REDIRECT_URI

print(URL)
```
```python
MYJOHNDEERE_V3_JSON_HEADERS = { 'Accept': 'application/vnd.deere.axiom.v3+json',
                                'Content-Type': 'application/vnd.deere.axiom.v3+json'}

# If your app happens to be already approved for production, then use the partnerapi.deere.com, otherwise stick with sandboxapi.deere.com
API_CATALOG_URI = 'https://sandboxapi.deere.com/platform/'
#API_CATALOG_URI = 'https://partnerapi.deere.com/platform/'

api_catalog_response = oauth2_session.get(API_CATALOG_URI, headers=MYJOHNDEERE_V3_JSON_HEADERS)   
# Test status code
api_catalog_response.status_code
# Test json response
api_catalog_response.json()

```

200 is a successful status response, and our response.json() code will create a json output.
Before we move forward, we will need to do some housekeeping. The json code that is produced from this code is not quite what we want. There is a slight difference in output that we'll want to address.The code below will clean up our previous output.

```python
### Clean Json Output with API Catalog

links_array_from_api_catalog_response = api_catalog_response.json()['links']
links_array_from_api_catalog_response
```
Now we want to do the same with our organizations, not just the API catalog.

```python
### Make the org link for Org Response

organizations_link = None

for link_object in links_array_from_api_catalog_response:
  if(link_object['rel'] == 'organizations'):
    organizations_link = link_object['uri']
    break;
    
organizations_link
```

```python
### Org Response OAuth2 (messy output) 

organizations_response = oauth2_session.get(organizations_link, headers = MYJOHNDEERE_V3_JSON_HEADERS)
organizations_response.json()
```

```python
### Clean Json Output with Org Response

links_array_from_api_org_response = organizations_response.json()['values']
links_array_from_api_org_response
```
If you want to do a deep dive on the purpose of this code, further exploration can be done here:

https://colab.research.google.com/github/JohnDeere/DevelopWithDeereNotebooks/blob/master/Onboarding/myjohndeere-api-onboarding.ipynb#scrollTo=sNKiFKDHWAwZ)

```python
### Connections Link

connections_link = None

for link_object in links_array_from_api_org_response:
  for links in link_object['links']:
    if(links['rel'] == 'connections'):
      connections_link = links['uri']
      break;
    
print(connections_link + "&redirect_uri=" + CLIENT_REDIRECT_URI)
```

Now we're going to want to take this output and put it into a dataframe so we can examine the data a little easier. Below is an example json output converted into table form. We'll need a few more packages as well.

```python
import numpy as np
import urllib3
from pandas.io.json import json_normalize
```

```python
url_example = [{'@type': 'Link',
  'rel': 'currentUser',
  'uri': 'https://sandboxapi.deere.com/platform/users/@currentUser'},
 {'@type': 'Link',
  'rel': 'organizations',
  'uri': 'https://sandboxapi.deere.com/platform/organizations'},
 {'@type': 'Link',
  'rel': 'agencies',
  'uri': 'https://sandboxapi.deere.com/platform/agencies'}]
#cars = pd.read_json(url_cars)
json_normalize(url_example)
```

Beautiful.

Next, we need to make an API call and download the file.







